Making all equalities equal

### 2021-09-21 paper.lagda.tex
created instances of equality

>>>>

\begin{code}
module Equalities {a ℓ} {A : Set a} where
  ≣-Type' = ≣-Type {a} {ℓ} {A}

  module _
    (_≡₁_ : ≣-Type')
    (_≡₂_ : ≣-Type')
    ⦃ eq₁ : IsEquality {a} {ℓ} _≡₁_ ⦄
    ⦃ eq₂ : IsEquality _≡₂_ ⦄
    where

    ℓ₁ = ℓ-max a ℓ

    record IsEquality₂ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
      constructor eq
      field
        ≣-≡-≡ : ∀ {x y} → let
          x≡y : Type ℓ₁
          x≡y = x ≡₁ y

      instance
        isEquality : IsEquality _≣_
        isEquality = eq (≣-≡-≡ ∙ IsEquality.≣-≡-≡ eq₁)

    instance
      ≡₂-Equality₂ : IsEquality₂ _≡₂_
      ≡₂-Equality₂ = eq (eq₂ .≣-≡-≡ ∙ sym (eq₁ .≣-≡-≡))
        where open IsEquality

    alwaysEqual : ∀ {x y} →  x ≡₁ y → x ≡₂ y
    alwaysEqual {x} {y} p =
      let joined = sym (≣-≡-≡ {x} {y})
      in transport joined p
      where open IsEquality₂ ≡₂-Equality₂

    module _
      (_≡₃_ : ≣-Type {ℓ-suc ℓ₁} {a})
      ⦃ eq₃ : IsEquality _≡₃_ ⦄
      where

      record IsEquality₃ (_≣_ : ≣-Type') : Set (ℓ-suc (ℓ-max a ℓ)) where
        constructor eq
        field
          ≣-≡-≡ : ∀ {x y} → let
            x≡y : Type ℓ₁
            x≡y = x ≡₁ y

            in x≣y ≡₃ x≡y

        instance
          isEquality₂ : IsEquality₂ _≣_
          isEquality₂ = eq (transport (IsEquality.≣-≡-≡ eq₃) ≣-≡-≡)

          isEquality : IsEquality _≣_
          isEquality = eq (IsEquality₂.≣-≡-≡ isEquality₂ ∙ IsEquality.≣-≡-≡ eq₁)

      instance
        ≡₂-Equality₃ : IsEquality₃ _≡₂_
        ≡₂-Equality₃ = eq α
          where
            open IsEquality eq₃
            α : ∀ {x y} → (x ≡₂ y) ≡₃ (x ≡₁ y)
            α {x} {y} = let
              α₁ = ≣-≡-≡ {x ≡₂ y} {x ≡₁ y}
              α₂ = IsEquality₂.≣-≡-≡ ≡₂-Equality₂ {x} {y}
              in transport (sym α₁) α₂

\end{code}
